Supplementary Information to: "Predicting Absolute Holocellulose and Klason Lignin Contents for Peat Remains Challenging

### 2022-03-03 analysis/paper/003-paper-m-gaussian-beta.Rmd
Cleanup.

# compute loos
m1.3_loo <- loo(m1.3, k_threshold = k_threshold)
m2.3_loo <- loo(m2.3, k_threshold = k_threshold)

# ---todo: brms and rstanarm yield very different uncertainty estimates. brms has smaller prediction intervals. The reason seems to be the different priors for phi (normal(0, 2.5) for rstanarm; gamma(0.01, 0.01) for brms).
```

>>>>

# compute loos
m1.3_loo <- loo(m1.3, k_threshold = k_threshold)
m2.3_loo <- loo(m2.3, k_threshold = k_threshold)
```
